### 2017-03-24 plt.tex
thickening lines

    \addplot[smooth] plot file {./lralp_exp/V_LP};
    \addplot[dashed] plot file {./lralp_exp/V_pol_CS};
    \addplot[dotted] plot file {./lralp_exp/V_pol_cone};
    \addlegendentry{$J^*$};
    \addlegendentry{$J_{CS}$};
    \addlegendentry{$J_{LRA}$};

>>>>

    \addplot[smooth,thick] plot file {./lralp_exp/V_LP};
    \addplot[dashed,thick] plot file {./lralp_exp/V_pol_CS};
    \addplot[dotted,thick] plot file {./lralp_exp/V_pol_cone};
    \addlegendentry{$J^*$};
    \addlegendentry{$J_{CS}$};
    \addlegendentry{$J_{LRA}$};
